---
title: "MTCARS MPG Explorer"
author: "Isi"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

## Product Pitch

`MTCARS MPG Explorer` is a small interactive Shiny app built for the Coursera course `Developing Data Products`.

Its goal is to turn the classic `mtcars` dataset into a quick exploration tool for fuel efficiency.

The app lets users:

- filtering cars by horsepower
- comparing automatic and manual transmission groups
- focusing on selected gear counts
- visualizing the relationship between car weight and fuel economy

## Why It Matters

Fuel economy is not driven by one variable alone.

Instead of reading a static table, users can interactively explore how vehicle weight, horsepower, gears, and transmission type influence miles per gallon.

This makes the app useful for:

- learning exploratory data analysis with a familiar dataset
- understanding simple relationships in automotive performance data
- seeing how filters change both plots and summary statistics in real time

## Built For Reproducibility

The app uses the built-in `mtcars` dataset, so it is fully reproducible without external downloads.

The deployed Shiny app is available here:

<https://img-mgt.shinyapps.io/mtcars-mpg-explorer/>

```{r}
summary(mtcars[, c("mpg", "hp", "wt", "gear")])
```

## Relationship In The Data

One of the clearest patterns in `mtcars` is that heavier cars tend to have lower fuel economy.

```{r echo=FALSE}
plot(
  mtcars$wt,
  mtcars$mpg,
  pch = 19,
  col = "#2C7FB8",
  xlab = "Weight (1000 lbs)",
  ylab = "Miles per gallon",
  main = "Weight and fuel economy in mtcars"
)
abline(lm(mpg ~ wt, data = mtcars), col = "#D95F0E", lwd = 2)
```

The regression line highlights the negative association between weight and MPG.

## Main Features

The Shiny app includes:

- a horsepower range slider
- transmission filters
- gear filters
- a plotted regression line
- a filtered table and summary statistics

Together, these features make the application a compact but effective interactive data product.
